Manuscript_Outputs

### 2024-01-24 Scripts/Stats_Analysis/RMarkdown/ManuscriptOutputs.Rmd
ROC plots are now time-dependent

# Pretty plots
library(etm)
library(plotROC) # For XML dependency, used install.packages("XML", type = "binary") to avoid compilation issues
library(gridExtra)
library(maps)
library(pROC)

@@

# ROC plot
# https://rviews.rstudio.com/2019/03/01/some-r-packages-for-roc-curves/
# https://cran.r-project.org/web/packages/plotROC/plotROC.pdf
# https://cran.r-project.org/web/packages/plotROC/vignettes/examples.html

# New approach uses pROC, Xiaonan's code
# https://gitlab.ndph.ox.ac.uk/jenniferco/prsondiabetes/-/blob/Riskscore/Scripts/Stats_Analysis/RMarkdown/RiskScore_Primary.Rmd#auc

roc_plot <- function(data, modelname, prsname, plotname,
                     varlist=c("gail_10risk_cal", "PRS_bc_std", "gail_prs_10risk")){

  AUC_CIs <- sapply(varlist, function(x) AUC_CI(df=data, score=x, status = "TEU_BrCa_status", dp=2))

  AUC_labels <- c(
    paste0(modelname, " 10-yr risk: ", AUC_CIs[1]),
    paste0(prsname, " PRS: ", AUC_CIs[2]),
    paste0(modelname, " & PRS 10-yr risk: ", AUC_CIs[3])
  )

  long <- data %>%
    select(ID, TEU_BrCa_status, all_of(varlist)) %>%
    pivot_longer(!c("ID","TEU_BrCa_status"), names_to = "Score", values_to = "Value") %>%
    mutate(Score=factor(Score,levels = varlist))

  plot <- ggplot(long, aes(d=TEU_BrCa_status, m=Value, color=Score)) +
    geom_roc(n.cuts = 0, linealpha = 1, size=1) +
    style_roc() +
    geom_abline(aes(slope=1, intercept=0), linetype="dashed") +
    scale_color_manual(name="AUC (95% CI)", labels =  AUC_labels, values = c("#F8766D","#00BA38", "#6193FF")) +
    labs(title = paste0(plotname), 
         caption = "Dashed line is y=x") +
    theme(legend.position = c(0.7, 0.15))

@@

# Tyrer-Cuzick
TC_roc <- roc_plot(test_data, modelname="TC", prsname="Genomics plc", plotname="Tyrer-Cuzick",
         varlist=c("TC_10risk_cal", "PRS_bc_std", "TC_prs_10risk"))

# Gail
gail_roc <- roc_plot(test_data, modelname="Gail", prsname="Genomics plc", plotname="Gail",
         varlist=c("gail_10risk_cal", "PRS_bc_std", "gail_prs_10risk"))

gridExtra::grid.arrange(TC_roc, gail_roc,
                        ncol=2,
                        top=paste0("ROC curves for 10-yr risk predictions in test data (N=", nrow(test_data), ")"))

>>>>

# Pretty plots
library(etm)
library(plotROC) # For XML dependency, used install.packages("XML", type = "binary") to avoid compilation issues
library(gridExtra)
library(maps)
library(timeROC)

@@

# Time-dependent ROC at 10 years, using timeROC

td_roc_plot <- function(data, modelname, prsname, plotname,
                     varlist=c("gail_10risk_cal", "PRS_bc_std", "gail_prs_10risk")){

  # Time-dependent ROC
  tROC <- lapply(varlist,
                 function(i) timeROC::timeROC(T=data$TEU_BrCa_time, 
                                              delta=data$TEU_BrCa_status, 
                                              marker=data[[i]],
                                              cause=1, times=c(9, 10), weighting="marginal"))

  tROC_long <- rbind(cbind(tROC[[1]][["TP"]], tROC[[1]][["FP"]]),
                     cbind(tROC[[2]][["TP"]], tROC[[2]][["FP"]]),
                     cbind(tROC[[3]][["TP"]], tROC[[3]][["FP"]]))
  colnames(tROC_long) <- c("TP_9", "TP_10", "FP_9", "FP_10")
  tROC_df <- data.frame(tROC_long)
  tROC_df$Model <- factor(c(rep(paste0(modelname, " 10-yr risk"), times=dim(tROC[[1]][["TP"]])[1]),
                     rep(paste0(prsname, " PRS"), times=dim(tROC[[2]][["TP"]])[1]),
                     rep(paste0(modelname, " & PRS 10-yr risk"), times=dim(tROC[[3]][["TP"]])[1])),
                     levels=c(paste0(modelname, " 10-yr risk"),
                              paste0(prsname, " PRS"),
                              paste0(modelname, " & PRS 10-yr risk")))

  plot <- ggplot(tROC_df,aes(x=FP_10, y=TP_10, color=Model))+
    geom_line(linewidth=1) + style_roc() +
    geom_abline(aes(slope=1, intercept=0), linetype="dashed") +
    xlab("False positive fraction") + ylab("True positive fraction") +
    scale_color_manual(name="Model",values = c("#F8766D","#00BA38", "#6193FF")) +
    labs(title =plotname, caption = "Dashed line is y=x")+
    theme(legend.position = c(0.75, 0.15))

@@

# Tyrer-Cuzick
TC_roc <- td_roc_plot(test_data, modelname="TC", prsname="Genomics plc", plotname="Tyrer-Cuzick",
         varlist=c("TC_10risk_cal", "PRS_bc_std", "TC_prs_10risk"))

# Gail
gail_roc <- td_roc_plot(test_data, modelname="Gail", prsname="Genomics plc", plotname="Gail",
         varlist=c("gail_10risk_cal", "PRS_bc_std", "gail_prs_10risk"))

gridExtra::grid.arrange(TC_roc, gail_roc,
                        ncol=2,
                        top=paste0("Time-dependent ROC curves at 10 years follow up in test data (N=", nrow(test_data), ")"))
